Autonomous Oceanographic Data Collection towards Estimating Excursion Sets of Vector-valued Random Fields

### 2020-06-16 section2.tex
Updates from Overleaf

\subsection{Background, Notation and Co-Kriging}
\label{sec:bg_and_notation}
Given a random field $\gp$ and (noisy) observations of some of its components at some points in the domain, one can predict the value of the field at some unobserved location $s\in \domain$ by using the conditional mean of $\gp[s]$, conditional on the data. This process is called (co-)kriging, and kriging equations precisely tell us how to compute conditional means and covariances conditional on an arbitrary dataset.
We will here present the most general form of cokriging, where one can include several observations (batch) at a time and 
observations at a given location $s \in \domain$ may only include a subset of the components of $\gp[s]\in\mathbb{R}^{\no}$ 
(heterotopic).

@@

Letting $\gp[s,\ell]$ denote the $\ell\text{-th}$ component of $\gp[s]$, $s\in \domain$ and $\ell \in \{1\dots,p\}$, we will call \textit{generalized location} the couple $x=(s,\ell)$. Given such a generalized location notation $x$,  the notation $\gp[x]$ will be used to denote $\gp[s,\ell]$.

This slight change of notation will allow us to think of $\gp$ as a scalar-valued Gaussian random field 
indexed by $D\times \{1\dots,p\}$, which will give the co-kriging equations a particularly simple form that parallels the one of univariate kriging. Due to the naturality of the concept of \textit{generalized location}, 
we will generally use the word \textit{location}, while \textit{spatial location} will be used to stress that we are talking about a point $s \in \domain$. In the following, the letter $x$ will be reserved for generalized locations, while the letters $s$ and $\ell$ will be used for spatial locations and response indices respectively.

@@

Given a dataset consisting of  $q$ observations at spatial locations $s_i \in \domain$ and response indices $l_i \in \lbrace 1, ..., \no\rbrace$, $i=1, ..., q$, we can concatenate the information needed to specify the dataset by using the notation
\begin{align*}
\bm{x}:=(\bm{s}, \bm{\ell}):= (x_1,\dots, x_q),~\text{with }x_i=(s_i,\ell_i).
\end{align*}
In general, boldface letters will be used to denote concatenated quantities corresponding to batches of observations. 
We can then also compactly denote the values of the field at those different locations by
\begin{align*}
\gp[\bm{x}]:=
\left(\gp[s_1,\ell_1], ...,
\gp[s_q,\ell_{q}]\right) \in \mathbb{R}^{q}.
\end{align*}
%
\subsubsection{Co-Kriging}
\label{sec:cokriging}
Assuming now that $n$ batches of observations are available, with respective sizes $q_1,\dots, q_n$, and that one wishes 
to predict $\gp[\bm{x}]$ for some batch of $q\geq 1$ generalized locations $\bm{x}=(\bm{s}, \bm{\ell})$, the (simple) 
cokriging mean would then amount to simple kriging with respect to a scalar-valued Gaussian random field indexed by 
$D\times \{1\dots,p\}$ and with covariance kernel $k(\bm{x}, \bm{x}')=K(\bm{s}, \bm{s}')_{\ell, \ell'}$, that is:
%
\begin{equation}
\mu_{[n]}(\bm{x})=\mu(\bm{x})+\lambda_{[n]}(\bm{x})^T (\mathbf{z}_{[n]}-\mu(\bm{x})),
\end{equation}
where $\mu$ is $Z$'s initial mean function, $\mathbf{z}_{[n]}$ stands for the ($\sum_{i=1}^n q_i$)-dimensional vector of 
observed responses of $Z$ at all considered generalized locations, and $\lambda_{[n]}(\bm{x})$ is a vector of weights 
equal to $k(\bm{x}_{[n]}, \bm{x}_{[n]})^{-1} k(\bm{x}_{[n]}, \bm{x})$ with $\bm{x}_{[n]}=(\bm{x}_1,\dots, \bm{x}_n)$, 
$k(\bm{x}_{[n]}, \bm{x}_{[n]})$ being assumed non-singular throughout the presentation. The co-kriging %(conditional) 
residual (cross-)covariance function (with respect to batches of generalized locations) can also be expressed in the same vein via
%
\begin{equation}
k_{[n]}(\bm{x},\bm{x}')=k(\bm{x},\bm{x}')-\lambda_{[n]}(\bm{x})^T k(\bm{x}_{[n]}, \bm{x}_{[n]}) \lambda_{{[n]}}(\bm{x}').
\end{equation}

@@

%\subsection{Expected classification criteria}

%{\bf{I have not done anything here - skip this, I think}}.

%Rather than minimizing expected variance one can aim at minimizing the classification probability of the excursion set: 
%$\min [p,(1-p) ]$, see e.g. \cite{lilleborge2016information}.

%Again, since the conditional mean is a linear in the data, we only have to look at the %relevant linear combination via $\bm_{\xi}=E(\bxi)$.
%See also \cite{bhattacharjya2013value}.

%\begin{equation}
%E(\min \{ p,(1-p)\})=\int \min P(\xi_1 \leq t, \xi_2 \leq s),[1-P(\xi_1 \leq t, \xi_2 \leq s)] p(E(\bxi)=) dE(\bxi)=,
%\end{equation}
%for the complementary probabilities, this is again evaluated by the corner regions for the block, and $\Phi_4()$ evaluations are required.

%In the end, this result is integrated over the spatial domain $x \in X$.

>>>>

\subsection{Background, Notation and Co-Kriging}
\label{sec:bg_and_notation}
Given a random field $\gp$ and (noisy) observations of some of its components at some points in the domain, one can predict the value of the field at some unobserved location $\spatloc\in \domain$ by using the conditional mean of $\gp[\spatloc]$, conditional on the data. This process is called (co-)kriging, and kriging equations precisely tell us how to compute conditional means and covariances conditional on an arbitrary dataset.
We will here present the most general form of cokriging, where one can include several observations (batch) at a time and 
observations at a given location $s \in \domain$ may only include a subset of the components of $\gp[\spatloc]\in\mathbb{R}^{\no}$ 
(heterotopic).

@@

Letting $\gp[\spatloc,\ell]$ denote the $\ell\text{-th}$ component of $\gp[\spatloc]$, $\spatloc\in \domain$ and $\ell \in \{1\dots,p\}$, we will call \textit{generalized location} the couple $x=(\spatloc,\ell)$. Given such a generalized location notation $x$,  the notation $\gp[x]$ will be used to denote $\gp[\spatloc,\ell]$.

This slight change of notation will allow us to think of $\gp$ as a scalar-valued Gaussian random field 
indexed by $D\times \{1\dots,p\}$, which will give the co-kriging equations a particularly simple form that parallels the one of univariate kriging. Due to the naturality of the concept of \textit{generalized location}, 
we will generally use the word \textit{location}, while \textit{spatial location} will be used to stress that we are talking about a point $\spatloc \in \domain$. In the following, the letter $x$ will be reserved for generalized locations, while the letters $\spatloc$ and $\ell$ will be used for spatial locations and response indices respectively.

@@

Given a dataset consisting of  $q$ observations at spatial locations $\spatloc_i \in \domain$ and response indices $l_i \in \lbrace 1, ..., \no\rbrace$, $i=1, ..., q$, we can concatenate the information needed to specify the dataset by using the notation
\begin{align*}
\bm{x}:=(\bm{\spatloc}, \bm{\ell}):= (x_1,\dots, x_q),~\text{with }x_i=(\spatloc_i,\ell_i).
\end{align*}
In general, boldface letters will be used to denote concatenated quantities corresponding to batches of observations. 
We can then also compactly denote the values of the field at those different locations by
\begin{align*}
\gp[\bm{x}]:=
\left(\gp[\spatloc_1,\ell_1], ...,
\gp[\spatloc_q,\ell_{q}]\right) \in \mathbb{R}^{q}.
\end{align*}
%
\subsubsection{Co-Kriging}
\label{sec:cokriging}
Assuming now that $n$ batches of observations are available, with respective sizes $q_1,\dots, q_n$, and that one wishes 
to predict $\gp[\bm{x}]$ for some batch of $q\geq 1$ generalized locations $\bm{x}=(\bm{\spatloc}, \bm{\ell})$, the (simple) 
cokriging mean would then amount to simple kriging with respect to a scalar-valued Gaussian random field indexed by 
$D\times \{1\dots,p\}$ and with covariance kernel $k(\bm{x}, \bm{x}')=K(\bm{\spatloc}, \bm{\spatloc}')_{\ell, \ell'}$, that is:
%
\begin{equation}
\mu_{[n]}(\bm{x})=\mu(\bm{x})+\lambda_{[n]}(\bm{x})^T (\mathbf{z}_{[n]}-\mu(\bm{x})),
\end{equation}
where $\mu$ is $Z$'s initial mean function, $\mathbf{z}_{[n]}$ stands for the ($\sum_{i=1}^n q_i$)-dimensional vector of 
observed responses of $Z$ at all considered generalized locations, and $\lambda_{[n]}(\bm{x})$ is a vector of weights 
equal to $k(\bm{x}_{[n]}, \bm{x}_{[n]})^{-1} k(\bm{x}_{[n]}, \bm{x})$ with $\bm{x}_{[n]}=(\bm{x}_1,\dots, \bm{x}_n)$, 
$k(\bm{x}_{[n]}, \bm{x}_{[n]})$ being assumed non-singular throughout the presentation. The co-kriging %(conditional) 
residual (cross-)covariance function (with respect to batches of generalized locations) can also be expressed in the same vein via
%
\begin{equation}
k_{[n]}(\bm{x},\bm{x}')=k(\bm{x},\bm{x}')-\lambda_{[n]}(\bm{x})^T k(\bm{x}_{[n]}, \bm{x}_{[n]}) \lambda_{{[n]}}(\bm{x}').
\end{equation}

@@
